Methods and Results

### 2021-02-27 ms.Rmd
New style file in yaml header

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: science.csl
  output: 
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: true
      reference_docx: template.docx
  editor_options: 
    chunk_output_type: console
---

>>>>

---
  title: "Methods and Results"
  author: 
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: pnas.csl
  output: 
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: true
      reference_docx: template.docx
  editor_options: 
    chunk_output_type: console
---
